# DistributionFitR


<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/DistributionFitR)](https://cran.r-project.org/package=dplyr)
<!-- badges: end -->

## Overview

DistributionFitR is an **autopilot**, which fits the **best distribution** in a set of distributions by maximizing the likelihood (MLE).

Parametric densities (or count densities) will be fitted to user-given **univariate** data via **maximum likelihood**. The user more or less only enters the data. The program automatically searches for **parametric distributions** and **parameters** thereof that best describe the data. It then returns the ten **best parameter families including the fitted parameters**. 

DistributionFitR comes in with a standard search list of **408 parametric distribution families** as given by R-packages on CRAN. The families can be adapted and increased to own packackages for special purposes.

## Installation
The **easiest way** to get DistribtionFitR is to install via CRAN
```{r, eval = FALSE}
install.packages("DistributionFitR")
```
To get a bug fix or to use a feature from the development version, you can install 
the development version of DistributionFitR from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("YCartes/DistributionFitR")
```

## Usage
```{r, message = FALSE}
library(DistributionFitR)
x <- rnorm(n = 1000, mean = 10, sd = 1)
r <- globalfit(x, packages = NULL, verbose = TRUE)

summary(r, n = 10)
hist(r)


r <- globalfit(rgamma(n = 1000, shape = 3, rate = 4))
summary(r, ic = "BIC")
summary(r, ic = "AICc")
summary(r, ic = "BIC", n = 7)
hist(r, ic = "BIC")
hist(r, ic = "BIC", which = 7)

AIC(r, n = 2)
BIC(r)
```

## Contribute
Read more [here](./private/how-to-contribute.md).
