# How To: Development Setup for Contribution

## Install Languages

- Install current version of R from [CRAN](https://cran.r-project.org/bin/windows/base/).
- Install current version of [Python 3](https://www.python.org/downloads/).
- Install current version of [Git](https://git-scm.com/downloads) and clone the Repository from [Git](https://github.com/YCartes/DistributionFitr) via ```git clone```.

## Install Tools

- Install current version of [Pandoc](https://pandoc.org/installing.html).
- Set environment variable ```RSTUDIO_PANDOC``` to the folder where you installed pandoc.
- Install [Poetry](https://python-poetry.org/docs/#installation/) as package manager for python.
- Install ```renv``` as package manager for R: Run ```install.packages("renv") ``` in R.

## Setup Environment with Package Manager
- Run the following files in the base of the project directory as working directory.
- Python Environment: Run ```poetry install``` in Terminal.
- R Environment: Run ```renv::init()```.

## Develop

Now you should be able to develop....enjoy it :)

## Testing

tbd
```{r, eval = FALSE}
devtools::load_all()
```

For further details refer to http://r-pkgs.had.co.nz/check.html.

## Commit your changes

If you changed one of the R-Markdown ```.Rmd``` files, the new Markdown  ````.md`` files must be generated. This is done by ```rmarkdown::render("input.Rmd", md_document(variant = "gfm"))``` in R.

Make sure you save your current environment to the lock file:
```{r, eval = FALSE}
renv::snapshot()
````

As you commit ```precommit``` is running automatically and checking your code.

tbd
